Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-27 JCB/conclusion_JCB.tex
updated conclusion

We validated our model on the 5s rRNA and 16s rRNA (See Sec.~\ref{sec:results}) and showed that our technology enables us to recover 
mutational errors with [INSERT PERFS]. Interestingly, we observed that using the isostericity matrices alone yields higher performance than with the 
nearest-neighbour energy model alone. This findings supports our hypothesis that isostericity matrices provide a valuable source of informations that
can be efficiently used for RNA sequence and structure analysis.

>>>>

We validated our model on the 5s rRNA and 16s rRNA (See Sec.~\ref{sec:results}) and showed that our technology enables us
to recover mutational errors with high accuracy (Area under the ROC curve between $0.95$ and $0.99$ when the mutations are
located in in base paired regions). Interestingly, we observed that using the isostericity matrices alone yields higher performance
than with the nearest-neighbour energy model alone. This finding supports our hypothesis that isostericity matrices provide a
valuable source of informations that can be efficiently used for RNA sequence and structure analysis. Nonetheless, we also found
that the nearest-neighbour model seems to provide a valuable signal when we under-estimate of the number of errors in the input
sequences.
